PAQ for parenting observational study

### 2017-05-31 joint_attention/parenting_obs_JA.Rmd
added demographics to ja analysis

```{r}
# demo <- read.csv("../parenting_obs_demo.csv")
conditions <- read.csv("conditions.csv")

d <- d.raw %>%
  left_join(conditions)%>%
  mutate(bids_tot = bids + cja + pja)
```

@@

>>>>

```{r}
conditions <- read.csv("conditions.csv")

load("../paq/paq_demo.RData")

ids$SID <- ids$sid

d <- d.raw %>%
  left_join(conditions)%>%
  mutate(bids_tot = bids + cja + pja)%>%
  left_join(ids)
```

@@

ggplot(ms_bids, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention") 
```

### 2017-05-31 paq/parenting_obs_paq.Rmd
added demographics to ja analysis

@@

demo <- demo %>%
  mutate(sid = SID)%>%
  select(sid, ethnicity, parent_ed)

@@

>>>>

paq_gd <- read.csv('paq_gdrive.csv')

@@

demo <- demo %>%
  mutate(sid = SID)%>%
  select(sid, ethnicity, parent_ed, num_lang, gender, age)

@@

Get data for individual differences analysis.
```{r}
ids <- dq %>%
  group_by(sid, category) %>%
  multi_boot_standard(col = "rating", na.rm = TRUE)%>%
  select(sid, category, mean)%>%
  spread(category, mean)%>%
  left_join(demo)

save(ids, file = "paq_demo.RData")
```
